Segmentation of Electron Microscopy Images for Connectomics

### 2018-04-27 papers/quals2018/paper.tex
Changed format and removed old text

	%%%%%%%%% TITLE
	\title{Biologically-Constrained Error Correction for Connectome Reconstruction}

	\author{Brian Matejek\\
	Harvard University\\
	Cambridge, MA 02138, USA\\
	{\tt\small bmatejek@seas.harvard.edu}
	%% For a paper whose authors are all at the same institution,
	%% omit the following lines up until the closing ``}''.
	%% Additional authors and addresses can be added with ``\and'',
	%% just like the second author.
	%% To save space, use either the email address or home page, not both
	%%\and
	%%Second Author\\
	%%Institution2\\
	%%First line of institution2 address\\
	%%{\tt\small secondauthor@i2.org}
	}

@@

	%%%%%%%%% ABSTRACT
	\begin{abstract}
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
	\end{abstract}
	%%%%%%%%	% BODY TEXT

@@

	\input{3_evaluation}

	\input{4_results}

>>>>

	%%%%%%%%% TITLE
	\title{Segmentation of Electron Microscopy Images for Connectomics}

	\author{Brian Matejek\\
		Advisor: Hanspeter Pfister \\
	Harvard University\\
	{\tt\small bmatejek@seas.harvard.edu}
	%% For a paper whose authors are all at the same institution,
	%% omit the following lines up until the closing ``}''.
	%% Additional authors and addresses can be added with ``\and'',
	%% just like the second author.
	%% To save space, use either the email address or home page, not both
	%%\and
	%%Second Author\\
	%%Institution2\\
	%%First line of institution2 address\\
	%%{\tt\small secondauthor@i2.org}
	}

@@

@@

	\input{3_results}

	\input{4_proposed}
